\documentclass{beamer}

% You can also use a 16:9 aspect ratio:
%\documentclass[aspectratio=169]{beamer}
\usetheme{TACC16}

% It's possible to move the footer to the right:
%\usetheme[rightfooter]{TACC16}

\begin{document}
\title[XALT]{XALT's Big Data Problem}
% page 1
\frame{\titlepage} 

% page 2
\begin{frame}{What is XALT 2?}
  \begin{itemize}
    \item XALT tracks links and executable runs on S1, S2 \& Maverick
    \item XALT has filter to avoid tracking every user executable
    \item XALT is being used at other sites in US, KAUST, etc.
  \end{itemize}
\end{frame}

% page 3
\begin{frame}{Current Design: Linking}
  \begin{itemize}
    \item XALT hijacks linker
    \item XALT's ld calls system ld
    \item XALT records: functions, linkA, resultT
    \item Each exe is ``watermarked'' $\Rightarrow$ gets a build uuid
    \item Code is added to run before and after main().
  \end{itemize}
\end{frame}

% page 4
\begin{frame}[fragile]
    \frametitle{Json Link example }
    {\tiny
\begin{semiverbatim}
\{
    "function": [],
    "linkA": [
        [ "/usr/lib64/librt-2.17.so", "1b8a16c..."  ],
        [ "/usr/lib64/libm-2.17.so",  "1030f25..."  ]
    ],
    "link_line": [ ],
    "resultT": \{
        "build_epoch": "1498754507.9059",
        "build_syshost": "stampede2",
        "build_user": "mclay",
        "exec_path": "/home1/00515/mclay/t/hello",
        "hash_id": "3eae43c0...,
        "link_path": "/opt/intel/.../icc",
        "link_program": "icc",
        "uuid": "b6e67891-9362-4ccd-8476-a08b9bd9898b",
        "wd": "/home1/00515/mclay/t"
    \}
\}
\end{semiverbatim}
    }
\end{frame}

% page 5
\begin{frame}{Current Design: run}
  \begin{itemize}
    \item Each run produces two json files: Start and End.
    \item Start record: Some program won't complete
    \item End record: Find run\_time
    \item Each json file: Environment, Shared libraries,
  \end{itemize}
\end{frame}

% page 6
\begin{frame}[fragile]
    \frametitle{Json Run example}
    {\tiny
\begin{semiverbatim}
\{
    "cmdlineA": []
    "envT": \{ ... \}
    "hash_id": "3eae43c087b90e0672ccdbe7f0d44058491274bf",
    "libA": [
        [ "/usr/lib64/librt-2.17.so", "1b8a16c..."  ],
        [ "/usr/lib64/libm-2.17.so",  "1030f25..."  ]
    ],
    "userDT": \{
        "end_time": 1498754913.81,
        "num_cores": 1.0,
        "num_nodes": 1.0,
        "num_threads": 1.0,
        "run_time": 0.166,
        "start_time": 1498754913.644
    \},
    "userT": \{
        "exec_path": "/home1/00515/mclay/t/hello",
        "exec_type": "binary",
        "job_id": "76064",
        "run_uuid": "acc1af54-6d3c-4ada-8cac-4c8f6aad8bb5",
        "user": "mclay"
    \},
    "xaltLinkT": \{
        "Build_Epoch": "1498754507.9059",
        "Build_UUID": "b6e67891-9362-4ccd-8476-a08b9bd9898b",
        "Build_User": "mclay",
    \}
\}
\end{semiverbatim}
    }
\end{frame}

% page 7
\begin{frame}{Optional Data collection}
  \begin{itemize}
    \item R libraries
    \item Python libraries
  \end{itemize}
\end{frame}

% page 8
\begin{frame}{1 to N relationships}
  \begin{itemize}
    \item Links
      \begin{itemize}
        \item functions
        \item libraries: *.a, *.so
      \end{itemize}
    \item Runs:
      \begin{itemize}
        \item Environment
        \item Shared libraries
        \item Python libraries (optionally)
        \item R libraries (optionally)
        \item ...
      \end{itemize}
  \end{itemize}
\end{frame}

% page 8
\begin{frame}{Kinds of queries}
  \begin{itemize}
    \item Top executables: num times, node-hours, unique users,
      /opt/apps executables
    \item Top libraries: num times, node-hours, unique users.
    \item Top users by node-hours, num times
    \item Top compiler usage by node-hours
    \item Top library usage from modules
  \end{itemize}
\end{frame}

% page 9
\begin{frame}{Current Installations}
  \begin{itemize}
    \item Stampede 2 is tracking MPI only.
    \item Maverick is both MPI and non-MPI.
    \item S2 is a big cluster.
    \item Maverick is a normal size cluster.
    \item In less than 10 days Maverick $>$ 5M runs
    \item Where as S2 > 40K runs (MPI only)
    \item August 23 has 64Gb syslog. 
    \item It has taken more than 4 days to process
    \item Written to a MYSQL db for each cluster.
    \item DB lives on XALT vm in the Rodeo VM farm.
  \end{itemize}
\end{frame}

% page 10
\begin{frame}{Maverick stats}
  \begin{itemize}
    \item 5M runs
    \item 10K runs $>$ 10 secs
    \item 0.2\% of runs take more than 10 secs.
  \end{itemize}
\end{frame}

% page 11
\begin{frame}{Needs}
  \begin{itemize}
    \item Must keep 1 to N relationships
    \item Need faster data ingestion
    \item Store some, Summerize when possible
    \item Multiple DB?: staging one to another?
  \end{itemize}
\end{frame}

% page 12
\begin{frame}{Questions}
  \begin{itemize}
    \item SQL db: MySQL, Postgresql?
    \item NO SQL db: Mongo? others?
  \end{itemize}
\end{frame}


\end{document}
