%* installation (deps, build/install procedure, making module/ml work)
%* configuration (either via ./configure at build time, or via 
%   $LMOD_FOO), most important configure options
%* setting up the system spider cache: configuring Lmod, updating spider 
%  cache, difference between system/user spider cache
%* + all (other) aspects mentioned on slide #26 in this slide deck: 
%   explained + example :)
%* what settarg is all about

\documentclass{beamer}

\usetheme[headernav]{TACC} %%Drop the 'headernav' if you don't like
                           %%the stuff at the top of your slide

\usepackage{amsmath,amssymb,amsthm}
\usepackage{alltt}
\usepackage{graphicx}

\title{XALT: Understanding HPC Usage via Job Level Collection}


\author{Robert McLay, Mark Fahey, Reuben Budiardja}
\institute{The Texas Advanced Computing Center, Argonne National Labs, NICS}

\date{February 8, 2017}  %% Use this if you want to fix the date in
                      %% stone rather than use \today

\newcommand{\bfnabla}{\mbox{\boldmath$\nabla$}}
\newcommand{\laplacian}[1]{\bfnabla^2 #1}
\newcommand{\grad}[1]{\bfnabla #1}
\newcommand{\tgrad}[1]{\bfnabla^T #1}
\newcommand{\dvg}[1]{\bfnabla \cdot #1}
\newcommand{\curl}[1]{\bfnabla \times #1}
\newcommand{\lap}[1]{\bfnabla^2 #1}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{XALT: What runs on the system}
  \begin{itemize}
    \item A U.S. NSF Funded project: PI: Mark Fahey and Robert McLay
    \item A Census of what programs and libraries are run
    \item Running at TACC, NICS, U. Florida, KAUST, ...
    \item Integrates with TACC-Stats.
  \end{itemize}
\end{frame}

\begin{frame}{Design Goals}
  \begin{itemize}
    \item Be extremely light-weight
    \item Provide provenance data: How?
    \item How many use a library or application?
    \item Collect Data into a Database for analysis.
  \end{itemize}
\end{frame}

\begin{frame}{Design: Linker}
  \begin{itemize}
    \item XALT wraps the linker to enable tracking of exec's
    \item The linker (ld) wrapper intercepts the user link line.
    \item Generate assembly code: key-value pairs
    \item Capture tracemap output from ld
    \item Transmit collected data in *.json format
  \end{itemize}
\end{frame}

\begin{frame}{Design: Launcher}
  \begin{itemize}
    \item XALT 1 used to require a wrapper for aprun, mpirun, etc
    \item XALT 2 no longer needs to
    \item Hooray! Correct wrappers were a nightmare!
  \end{itemize}
\end{frame}

\begin{frame}{Design: Transmission to DB}
  \begin{itemize}
    \item File: collect nightly
    \item Syslog: Use Syslog filtering (or ELK)
    \item Direct to DB.
    \item Future: RabbitMQ
  \end{itemize}
\end{frame}

\begin{frame}{Lmod to XALT connection}
  \begin{itemize}
    \item Lmod spider walks entire module tree.
    \item Can build a reverse map from paths to modules
    \item Can map program \& libraries to modules.
    \item /opt/apps/i15/mv2\_2\_1/phdf5/1.8.14/lib/libhdf5.so.9
      $\Rightarrow$ phdf5/1.8.14(intel/15.02:mvapich2/2.1)
    \item Also helps with function tracking.
    \item Tmod Sites can still use Lmod to build the reverse map.
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
    \frametitle{Database Changes (I)}
  \begin{itemize}
      \item Tables sizes in XALT:
 {\small
    \begin{alltt}
+------------------+------------+
| Table            | Size in MB |
+------------------+------------+
| join_run_env     |  199603.00 |
| join_run_object  |    9388.00 |
| join_link_object |    5013.00 |
| xalt_run         |    4613.00 |
| xalt_object      |    4175.00 |
| xalt_link        |     814.00 |
+------------------+------------+
    \end{alltt}
}
    \item \texttt{join\_run\_env} has 2.1 billion rows
  \end{itemize}
\end{frame}

\begin{frame}{Database Changes (II)}
  \begin{itemize}
    \item Environment variables are important.
    \item But mainly for reproducing results
    \item Chose a few for SQL tests.
  \end{itemize}
\end{frame}

\begin{frame}{Database Changes (III): New Design}
  \begin{itemize}
    \item Store complete env $\Rightarrow$ compressed json blob
    \item Filter Env's with Accept Test followed by Reject Test
    \item Instead of 250 vars per job $\Rightarrow$ 20 to 30.
    \item The Filter is site controllable!
  \end{itemize}
\end{frame}

\begin{frame}{Database Changes (IV): New Design}
  \begin{itemize}
    \item The ``join'' tables are large 
    \item Partition ``join'' tables by dates or index
    \item Precompute views nightly.
  \end{itemize}
\end{frame}

\begin{frame}{Protecting XALT (I): UTF8 Characters}
  \begin{itemize}
    \item Linux supports UTF8 Characters in file names, env. vars.
    \item Python supports UTF8 if you know what you are doing.
    \item Switch XALT to use prepared statements
    \item Where \texttt{query="INSERT INTO table VALUE(?,?)"}
    \item This prevent SQL injection: ``johnny drop tables;''
    \item Also supports UTF8 characters.
  \end{itemize}
\end{frame}

\begin{frame}{Protecting XALT (II): Python to C++}
    \begin{itemize}
      \item Difficult to protect Python from users in every case
      \item Solution: LD\_LIBRARY\_PATH="@ld\_lib\_path@"
        PATH=/usr/bin:/bin C++-exec ...
      \item Everything that depends on PATH must be hard coded
      \item basename $\Rightarrow$ /bin/basename
      \item Unique install for each operating system.
      \item Certain programs aren't in the same place: \texttt{basename}
    \end{itemize}
\end{frame}

\begin{frame}{Using XALT Data}
  \begin{itemize}
    \item Targetted Outreach: Who will be affected
    \item Largemem Queue Overuse
    \item XALT and TACC-Stats
  \end{itemize}
\end{frame}

\begin{frame}{Tracking Non-mpi jobs (I)}
  \begin{itemize}
    \item Originally we tracked only MPI Jobs
    \item By hijacking mpirun etc.
    \item Now we can use ELF binary format to track jobs
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
    \frametitle{ELF Binary Format Trick}
 {\small
    \begin{alltt}
void myinit(int argc, char **argv)
\{
  /* ... */
\}
void myfini()
\{
  /* ... */
\}
  __attribute__((section(".init_array")))
       typeof(myinit) *__init = myinit;
  __attribute__((section(".fini_array")))
       typeof(myfini) *__fini = myfini;
    \end{alltt}
}
\end{frame}

\begin{frame}{Using the ELF Binary Format Trick}
  \begin{itemize}
    \item This C code is compiled and linked in through the hijacked linker
    \item It can also be used with \texttt{LD\_PRELOAD}
    \item We are using both...
  \end{itemize}
\end{frame}

\begin{frame}{Downsides}
  \begin{itemize}
    \item Currently, we only track task 0 jobs.
    \item MPMD programs will only record the Task 0 job.
    \item We also lose the ability to capture return exit status
  \end{itemize}
\end{frame}

\begin{frame}{Challenges (I)}
  \begin{itemize}
    \item Do not want to track mv, cp, etc
    \item Only want to track some executables on compute nodes
    \item Do not want to get overwhelmed by the data. 
  \end{itemize}
\end{frame}

\begin{frame}{Answers}
  \begin{itemize}
    \item XALT Tracking only when told to
    \item Compute node only by host name filtering
    \item Executable Filter based on Path
    \item Protection against closing stderr before fini.
    \item Site configurable!
  \end{itemize}
\end{frame}

\begin{frame}{Path Filtering}
  \begin{itemize}
    \item Accept test, following an Ignore Test,
    \item Two files containing regex patterns, converted to code.
    \item Accept List Tests: Track /usr/bin/ddt, /bin/tar
    \item Ignore List Tests: /usr/bin, /bin, /sbin, ...
  \end{itemize}
\end{frame}

\begin{frame}{Using XALT 2}
  \begin{itemize}
    \item A great deal of hardening 
    \item Been running XALT 2 for 4 months with only 1 tckt.
  \end{itemize}
\end{frame}

\begin{frame}{Speeding up XALT 2}
  \begin{itemize}
    \item XALT 2 generates 2 json records: at start and end
    \item Want to minimize measurement: Launcher jobs
    \item The most expensive operation is sha1sum of the shared libs
    \item Used to system sha1sum call in serial
    \item Now up-to 16 threads calls directly
    \item Tests show 1 sec first time 0.04 second time on Lustre.
  \end{itemize}
\end{frame}


\begin{frame}{XALT Demo}
  \begin{itemize}
    \item Show modules hierarchy
    \item ml --raw show xalt
    \item Show debugging output
    \item type -a {ld,mpirun}
    \item Build programs
    \item Run tests
    \item Run utf8 program
    \item Show database results
  \end{itemize}
\end{frame}

\begin{frame}{Conclusion}
  \begin{itemize}
    \item Lmod:
      \begin{itemize}
        \item Source: github.com/TACC/lmod.git, lmod.sf.net
        \item Documentation: lmod.readthedocs.org
      \end{itemize}
    \item XALT:
      \begin{itemize}
        \item Source: github.com/xalt/xalt.git, xalt.sf.net
        \item Documentation: doc/*.pdf, xalt.readthedocs.org
      \end{itemize}
  \end{itemize}
\end{frame}

\end{document}
