%* installation (deps, build/install procedure, making module/ml work)
%* configuration (either via ./configure at build time, or via 
%   $LMOD_FOO), most important configure options
%* setting up the system spider cache: configuring Lmod, updating spider 
%  cache, difference between system/user spider cache
%* + all (other) aspects mentioned on slide #26 in this slide deck: 
%   explained + example :)
%* what settarg is all about

\documentclass{beamer}

\usetheme[headernav]{TACC} %%Drop the 'headernav' if you don't like
                           %%the stuff at the top of your slide

\usepackage{amsmath,amssymb,amsthm}
\usepackage{alltt}
\usepackage{graphicx}

\title{XALT: Understanding HPC Usage via Job Level Collection}


\author{Robert McLay, Mark Fahey, Reuben Budiardja, Sandra Sweat}
\institute{The Texas Advanced Computing Center, Argonne National Labs, NICS}

\date{June 22, 2016}  %% Use this if you want to fix the date in
                      %% stone rather than use \today

\newcommand{\bfnabla}{\mbox{\boldmath$\nabla$}}
\newcommand{\laplacian}[1]{\bfnabla^2 #1}
\newcommand{\grad}[1]{\bfnabla #1}
\newcommand{\tgrad}[1]{\bfnabla^T #1}
\newcommand{\dvg}[1]{\bfnabla \cdot #1}
\newcommand{\curl}[1]{\bfnabla \times #1}
\newcommand{\lap}[1]{\bfnabla^2 #1}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\section{XALT}

\begin{frame}{XALT: What runs on the system}
  \begin{itemize}
    \item A U.S. NSF Funded project: PI: Mark Fahey and Robert McLay
    \item A Census of what programs and libraries are run
    \item Running at TACC, NICS, U. Florida, KAUST, ...
    \item Integrates with TACC-Stats.
  \end{itemize}
\end{frame}

\begin{frame}{Design Goals}
  \begin{itemize}
    \item Be extremely light-weight
    \item Provide provenance data: How?
    \item How many use a library or application?
    \item Collect Data into a Database for analysis.
  \end{itemize}
\end{frame}

\begin{frame}{Design: Linker }
  \begin{itemize}
    \item The linker (ld) wrapper intercepts the user link line.
      \begin{itemize}
        \item A shell script wrapper, \texttt{ld} which uses python
          scripts
        \item Generate assembly code: key-value pairs
        \item Capture tracemap output from ld
        \item Transmit collected data in *.json format
      \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{Design: Launcher}
  \begin{itemize}
    \item Program Launcher: mpirun, aprun, ibrun ...
      \begin{itemize}
        \item A shell script wrapper is called which uses python scripts
        \item Find Executable by parsing command
        \item Collect executable info, shared libraries, env.
        \item Transmit collected data in *.json format
      \end{itemize}
    \item The future is now.  This is nolonger necessary!
  \end{itemize}
\end{frame}

\begin{frame}{Design: Transmission to DB}
  \begin{itemize}
    \item File: collect nightly
    \item Syslog: Use Syslog filtering
    \item Direct to DB.
  \end{itemize}
\end{frame}

\begin{frame}{Lmod to XALT connection}
  \begin{itemize}
    \item Sites can use Tmod but use Lmod to help with XALT
    \item Lmod spider walks entire module tree.
    \item Can build A Reverse Map from paths to modules
    \item Can map program \& libraries to modules.
    \item /opt/apps/i15/mv2\_2\_1/phdf5/1.8.14/lib/libhdf5.so.9
      $\Rightarrow$ phdf5/1.8.14(intel/15.02:mvapich2/2.1)
    \item Also helps with function tracking.
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
    \frametitle{Database Changes (I)}
  \begin{itemize}
      \item Tables sizes in XALT:
 {\small
    \begin{alltt}
+------------------+------------+
| Table            | Size in MB |
+------------------+------------+
| join_run_env     |  199603.00 |
| join_run_object  |    9388.00 |
| join_link_object |    5013.00 |
| xalt_run         |    4613.00 |
| xalt_object      |    4175.00 |
| xalt_link        |     814.00 |
+------------------+------------+
    \end{alltt}
}
    \item \texttt{join\_run\_env} has 2.1 billion rows
  \end{itemize}
\end{frame}

\begin{frame}{Database Changes (II)}
  \begin{itemize}
    \item Environment variables are important.
    \item But mainly for reproducing results
    \item Not SQL tests (mostly)
  \end{itemize}
\end{frame}

\begin{frame}{Database Changes (III): New Design}
  \begin{itemize}
    \item Store complete env $\Rightarrow$ compressed json blob
    \item Filter Env's with Accept Test followed by Reject Test
    \item Instead of 250 vars per job $\Rightarrow$ 10!
    \item The Filter is site controllable.
  \end{itemize}
\end{frame}

\begin{frame}{Database Changes (IV): New Design}
  \begin{itemize}
    \item The ``join'' tables are large 
    \item Partition ``join'' tables by dates or index
    \item Precompute views nightly.
  \end{itemize}
\end{frame}

\begin{frame}{Protecting XALT (I): UTF8 Characters}
  \begin{itemize}
    \item Linux supports UTF8 Characters in file names, env. vars.
    \item Python supports UTF8 if you know what you are doing.
    \item Switch XALT to use prepared statements
    \item Where \texttt{query="INSERT INTO table VALUE(?,?)"}
    \item This prevent SQL injection: ``johnny drop tables;''
    \item Also supports UTF8 characters.
  \end{itemize}
\end{frame}

\begin{frame}{Protecting XALT (II): Python to C++}
    \begin{itemize}
      \item Difficult to protect python from users in every case
      \item Solution: LD\_LIBRARY\_PATH="@ld\_lib\_path@"
        PATH=/usr/bin:/bin C++-exec ...
      \item Everything that depends on PATH must be hard coded
      \item basename $\Rightarrow$ /bin/basename
      \item Unique install for each operating system.
      \item Programs move around: basename
    \end{itemize}
\end{frame}

\begin{frame}{Using XALT Data}
  \begin{itemize}
    \item Targetted Outreach: Who will be affected
    \item Largemem Queue Overuse
    \item XALT and TACC-Stats
  \end{itemize}
\end{frame}

\begin{frame}{Publishing XALT Data}
  \begin{itemize}
    \item Student Sandra Sweat
    \item Sanitized Data
    \item Community Codes Reported: Vasp*, WRF*, OpenFOAM*,
    \item users names : U012354, Charge Accounts: A12345
    \item Unique mapping, Added Field of Science
  \end{itemize}
\end{frame}

\begin{frame}{XALT Report Script (I)}
  \begin{itemize}
    \item Currently MPI only tracking
    \item About 70\% of Core-hours
    \item About 50\% of Jobs
  \end{itemize}
\end{frame}

\begin{frame}{XALT Report Script (II)}
  \begin{itemize}
    \item Over MPI Job Counts: User vs System
    \item Self Build vs Build User $\neq$ Run User
    \item Top MPI Executables
    \item Compiler Usage: C/C++ vs Fortran
    \item Library usage
  \end{itemize}
\end{frame}

\begin{frame}{Tracking Non-mpi jobs (I)}
  \begin{itemize}
    \item Originally we tracked only MPI Jobs
    \item By hijacking mpirun etc.
    \item Now we can use ELF binary format to track jobs
    \item This is the XALT 2 project.
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
    \frametitle{ELF Binary Format Trick}
 {\small
    \begin{alltt}
void myinit(int argc, char **argv)
\{
  /* ... */
\}
void myfini()
\{
  /* ... */
\}
  __attribute__((section(".init_array")))
       typeof(myinit) *__init = myinit;
  __attribute__((section(".fini_array")))
       typeof(myfini) *__fini = myfini;
    \end{alltt}
}
\end{frame}

\begin{frame}{Using the ELF Binary Format Trick}
  \begin{itemize}
    \item This C code is compiled and linked in through the hijacked linker
    \item It can also be used with \texttt{LD\_PRELOAD}
    \item We are using both...
  \end{itemize}
\end{frame}

\begin{frame}{New Features to XALT 2}
  \begin{itemize}
    \item Track task 0 programs.
    \item Track Non-MPI programs
    \item Track program not built under XALT.
    \item Support for 32 bit applications.
  \end{itemize}
\end{frame}


\begin{frame}{Other Safety Features}
  \begin{itemize}
    \item XALT Tracking only told to
    \item Compute node only
    \item Filter based on Path
    \item Protection against closing stderr before fini.
    \item Site configurable!
  \end{itemize}
\end{frame}

\begin{frame}{Path Filtering}
  \begin{itemize}
    \item Accept test, following an Ignore Test,
    \item Two files containing regex patterns, converted to code.
    \item Accept List Tests: Track /usr/bin/ddt, /bin/tar
    \item Ignore List Tests: /usr, /bin, /sbin, ...
    \item Filter out mv, cp, compilers, etc.
  \end{itemize}
\end{frame}

\begin{frame}{XALT 2 Status}
  \begin{itemize}
    \item Currently in alpha testing at TACC
    \item Testing new Database features
    \item New Design for CheckExec
  \end{itemize}
\end{frame}

\begin{frame}{CheckExec}
  \begin{itemize}
    \item At TACC we require Build Env. match Submit Env.
    \item Must have the similar compiler and mpi modules loaded.
    \item Do other sites require the same?
  \end{itemize}
\end{frame}

\begin{frame}{CheckExec Questions}
  \begin{itemize}
    \item Sites running modules?
    \item Build Env. matches Submit Env?
    \item Would a CheckExec tool be helpful?
  \end{itemize}
\end{frame}


\begin{frame}{XALT Demo}
  \begin{itemize}
    \item Show modules hierarchy
    \item ml --raw show xalt
    \item Show debugging output
    \item type -a {ld,mpirun}
    \item Build programs
    \item Run tests
    \item Run utf8 program
    \item Show database results
  \end{itemize}
\end{frame}

\section{Conclusion}
\begin{frame}{Conclusion}
  \begin{itemize}
    \item Lmod:
      \begin{itemize}
        \item Source: github.com/TACC/lmod.git, lmod.sf.net
        \item Documentation: lmod.readthedocs.org
      \end{itemize}
    \item XALT:
      \begin{itemize}
        \item Source: github.com/Fahey-McLay/xalt.git, xalt.sf.net
        \item Documentation: doc/*.pdf, xalt.readthedocs.org
      \end{itemize}
  \end{itemize}
\end{frame}

\end{document}
