%* installation (deps, build/install procedure, making module/ml work)
%* configuration (either via ./configure at build time, or via 
%   $LMOD_FOO), most important configure options
%* setting up the system spider cache: configuring Lmod, updating spider 
%  cache, difference between system/user spider cache
%* + all (other) aspects mentioned on slide #26 in this slide deck: 
%   explained + example :)
%* what settarg is all about

\documentclass{beamer}

\usetheme[headernav]{TACC} %%Drop the 'headernav' if you don't like
                           %%the stuff at the top of your slide

\usepackage{amsmath,amssymb,amsthm}
\usepackage{alltt}
\usepackage{graphicx}

\title{ XALT, OGRT and Related Technologies: Job-Level Usage Data on Today's Supercomputers}


\author{Robert McLay, Georg Rath}
\institute{The Texas Advanced Computing Center, NERSC}

\date{November 14, 2017}  %% Use this if you want to fix the date in
                      %% stone rather than use \today

\newcommand{\bfnabla}{\mbox{\boldmath$\nabla$}}
\newcommand{\laplacian}[1]{\bfnabla^2 #1}
\newcommand{\grad}[1]{\bfnabla #1}
\newcommand{\tgrad}[1]{\bfnabla^T #1}
\newcommand{\dvg}[1]{\bfnabla \cdot #1}
\newcommand{\curl}[1]{\bfnabla \times #1}
\newcommand{\lap}[1]{\bfnabla^2 #1}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{XALT: What runs on the system}
  \begin{itemize}
    \item A Census of what programs and libraries are run
    \item Running at TACC, NICS, U. Florida, KAUST, ...
    \item Integrates with TACC-Stats.
    \item Has commercial support from Ellexus 
  \end{itemize}
\end{frame}

\begin{frame}{History of XALT}
  \begin{itemize}
    \item Mark Fahey (was NICS, now ANL): ALT-D (MPI only)
    \item Robert McLay (TACC) Lariat (MPI only)
    \item Reuben Budiardja (was NICS now ORL)
    \item ALT-D $+$ Lariat $\Rightarrow$ XALT 1: (MPI only)
    \item XALT 2: All programs
  \end{itemize}
\end{frame}

\begin{frame}{Design Goals}
  \begin{itemize}
    \item Be extremely light-weight
    \item Provide provenance data: How?
    \item How many use a library or application?
    \item Collect Data into a Database for analysis.
  \end{itemize}
\end{frame}

\begin{frame}{Understanding what your users are doing}
  \begin{itemize}
    \item What programs, libraries are your users using?
    \item What are the top programs by node-hours? by counts?
    \item Are they building their own programs or using someone elses?
    \item Are Executables implemented in C/C++/Fortran?
    \item Track MPI: tasks? nodes?
    \item Track Threading via \$OMP\_NUMTHREADS
  \end{itemize}
\end{frame}

\begin{frame}{Design: Linker}
  \begin{itemize}
    \item XALT wraps the linker to enable tracking of exec's
    \item The linker (ld) wrapper intercepts the user link line.
    \item Generate assembly code: key-value pairs
    \item Capture tracemap output from ld
    \item Transmit collected data in *.json format
    \item Adds codes that executes before main() and after main() completes
  \end{itemize}
\end{frame}

\begin{frame}{Design: Transmission to DB}
  \begin{itemize}
    \item File: collect nightly
    \item Syslog: Use Syslog filtering (or ELK)
    \item Direct to DB. (Not in XALT 2)
    \item Future: RabbitMQ
  \end{itemize}
\end{frame}

\begin{frame}{Lmod to XALT connection}
  \begin{itemize}
    \item Lmod spider walks entire module tree.
    \item Can build a reverse map from paths to modules
    \item Can map program \& libraries to modules.
    \item /opt/apps/i15/mv2\_2\_1/phdf5/1.8.14/lib/libhdf5.so.9
      $\Rightarrow$ phdf5/1.8.14(intel/15.02:mvapich2/2.1)
    \item Also helps with function tracking.
    \item Tmod Sites can still use Lmod to build the reverse map.
  \end{itemize}
\end{frame}

\begin{frame}{Protecting XALT: Python to C++}
    \begin{itemize}
      \item XALT 1 used python scripts
      \item It was difficult to protect Python from users in everytime
      \item Solution: LD\_LIBRARY\_PATH="@ld\_lib\_path@"
        PATH=/usr/bin:/bin C++-exec ...
      \item Everything that depends on PATH must be hard coded
    \end{itemize}
\end{frame}

\begin{frame}{Using XALT Data}
  \begin{itemize}
    \item Targetted Outreach: Who will be affected
    \item Largemem Queue Overuse
    \item XALT and TACC-Stats
  \end{itemize}
\end{frame}

\begin{frame}{Tracking Non-mpi jobs (I)}
  \begin{itemize}
    \item Originally we tracked only MPI Jobs
    \item By hijacking mpirun etc.
    \item Now we can use ELF binary format to track jobs
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
    \frametitle{ELF Binary Format Trick}
 {\small
    \begin{alltt}
void myinit(int argc, char **argv)
\{
  /* ... */
\}
void myfini()
\{
  /* ... */
\}
  __attribute__((section(".init_array")))
       typeof(myinit) *__init = myinit;
  __attribute__((section(".fini_array")))
       typeof(myfini) *__fini = myfini;
    \end{alltt}
}
\end{frame}

\begin{frame}{Using the ELF Binary Format Trick}
  \begin{itemize}
    \item This C code is compiled and linked in through the hijacked linker
    \item It can also be used with \texttt{LD\_PRELOAD}
    \item We are using both...
  \end{itemize}
\end{frame}

\begin{frame}{Challenges (I)}
  \begin{itemize}
    \item Do not want to track mv, cp, etc
    \item Only want to track some executables on compute nodes
    \item Do not want to get overwhelmed by the data. 
  \end{itemize}
\end{frame}

\begin{frame}{Answers}
  \begin{itemize}
    \item XALT Tracking only when told to
    \item Compute node only by host name filtering
    \item Executable Filter based on Path
    \item Protection against closing stderr before fini.
    \item Site configurable!
  \end{itemize}
\end{frame}

\begin{frame}{Path Filtering}
  \begin{itemize}
    \item Accept test, following an Ignore Test,
    \item Two files containing regex patterns, converted to code.
    \item Accept List Tests: Track /usr/bin/ddt, /bin/tar
    \item Ignore List Tests: /usr/bin, /bin, /sbin, ...
    \item Uses FLEX to compile in patterns
  \end{itemize}
\end{frame}


\begin{frame}[fragile]
    \frametitle{TACC\_config.py}
 {\small
    \begin{alltt}
hostname_patterns = [
  ['KEEP', '^c[0-9][0-9][0-9]-[0-9][0-9][0-9]\..*']
  ]
path_patterns = [
    ['SPSR',  r'.*/python[0-9][^/][^/]*'],
    ['SPSR',  r'.*/R'],
    ['KEEP',  r'^/usr/bin/ddt'],
    ['SKIP',  r'^/usr/.*'],
    ['SKIP',  r'^/bin/.*'],
  ]
env_patterns = [
    [ 'SKIP', r'^MKLROOT=.*' ],
    [ 'SKIP', r'^MKL_DIR=.*' ],
    [ 'KEEP', r'^I_MPI_INFO_NUMA_NODE_NUM=.*'],
  ]
    \end{alltt}
}
\end{frame}



%\begin{frame}{Speeding up XALT 2}
%  \begin{itemize}
%    \item XALT 2 generates 2 json records: at start and end
%    \item Want to minimize measurement: Launcher jobs
%    \item The most expensive operation is sha1sum of the shared libs
%    \item Used to system sha1sum call in serial
%    \item Now up-to 16 threads calls directly
%    \item Tests show 1 sec first time 0.04 second time on Lustre.
%  \end{itemize}
%\end{frame}

\begin{frame}{Speeding up XALT 2}
  \begin{itemize}
    \item Minimal impact on jobs ($>$ 0.09 secs)
    \item Non-mpi jobs only produce end record
    \item Filter by job\_id after transport.
    \item No more than 100 executions per job\_id.  (Changable)
    \item A launcher job 5 million executions in two hours.
  \end{itemize}
\end{frame}

\begin{frame}{Tracking R packages}
  \begin{itemize}
    \item XALT 2 can now track R package usage
    \item James McComb \& Michael Scott from IU developed the R part
    \item They do this by intercepting the ``imports''
    \item Still in preliminary stages
    \item Plan to support Python later.
  \end{itemize}
\end{frame}

\begin{frame}{New program: xalt\_extract\_record}
  \begin{itemize}
    \item This program reads the watermark.
    \item Find out who built this program on what machine
    \item Find out what modules where used.
  \end{itemize}
\end{frame}

\begin{frame}[fragile]
    \frametitle{Example of xalt\_extract\_record output}
 {\small
    \begin{alltt}
****************************************
XALT Watermark: hello
****************************************
Build_Epoch              1510257139.4624
Build_LMFILES            /opt/apps/modulefiles/intel/17.0.4.lua:...
Build_LOADEDMODULES      intel/17.0.4:impi/17.0.3:python/2.7.13:TACC:...
Build_OS                 Linux 3.10.0-514.26.2.el7.x86_64
Build_Syshost            stampede2
Build_UUID               586d5943-67eb-480b-a2fe-35e87a1f22c7
Build_User               mclay
Build_compiler           icc
Build_date               Thu Nov 09 13:52:19 2017
Build_host               c455-011.stampede2.tacc.utexas.edu
XALT_Version             1.7.7-devel
    \end{alltt}
}
\end{frame}


\begin{frame}{Conclusion}
  \begin{itemize}
    \item Lmod:
      \begin{itemize}
        \item Source: github.com/TACC/lmod.git, lmod.sf.net
        \item Documentation: lmod.readthedocs.org
      \end{itemize}
    \item XALT:
      \begin{itemize}
        \item Source: github.com/Fahey-McLay/xalt.git, xalt.sf.net
        \item Documentation: doc/*.pdf, xalt.readthedocs.org
        \item Commercial support from Ellexus: www.ellexus.com/products/xalt-tracking-job-level-activity-supercomputers
      \end{itemize}
  \end{itemize}
\end{frame}

\end{document}
